---
title: "McDonald's Menu Analysis"
output: html_document
date: "2022-10-06"
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "../"
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(here)
library(janitor)
menu_data <- read_csv(here("data", "menu.csv")) %>%
  clean_names()
```


# Data

|variable|description|
|------|--------------|
|cholesterol|Measure of cholesterol levels in each item|
|carbohydrates|Measure of carbohydrate levels in each item|
|sugars|Measure of sugar levels in each item|

# EDR

## Items with the highest cholesterol
  I was curious to see what menu items had the highest levels of cholesterol. So I sorted the items according to cholesterol levels, and took the 10 highest values.
  
```{r}
cholesterol_levels <- menu_data %>%
  select(category, item, cholesterol) %>%
  group_by(category)

highest_cholesterol <- cholesterol_levels %>%
  arrange(desc(cholesterol))%>%
  head(10) %>% ggplot(aes(cholesterol, reorder(item, cholesterol), fill = item)) +
  geom_col() +
  geom_text(aes(label = cholesterol), position=position_stack(vjust=0.5),color="black",size=3) +
  ggtitle("McDonald's Top 10 Item with Highest Cholesterol Content") +
  theme(legend.position="none")

highest_cholesterol
```

 As soon as I saw the chart, I noticed that all the highest values belonged to the breakfast category. Which isn't that surprising when you consider that all of these items have eggs in them.
 
## Items with the highest carbohydrates

```{r}
carbohydrates_levels <- menu_data %>%
  select(category, item, carbohydrates) %>%
  group_by(category)

highest_carbohydrates <- carbohydrates_levels %>%
  arrange(desc(carbohydrates))%>%
  head(10) %>% ggplot(aes(carbohydrates, reorder(item, carbohydrates), fill = item)) +
  geom_col()+
  geom_text(aes(label = carbohydrates), position=position_stack(vjust=0.5),color="black",size=3)+
  ggtitle("McDonald's Top 10 Item with Highest Carbohydrates Content") +
  theme(legend.position="none")

highest_carbohydrates
```

  Looking at the graph above, we observe that milkshakes make a majority of have very high levels of carbohydrates in comparison to drinks from other categories. So we can conclude that milkshakes are a bad choice for a drink while having a meal that is already high in carbohydrates.

## Items with the highest sugar

```{r}
sugar_levels <- menu_data %>%
  select(category, item, sugars) %>%
  group_by(category)

highest_sugar <- sugar_levels %>%
  arrange(desc(sugars))%>%
  head(10) %>% ggplot(aes(sugars, reorder(item, sugars), fill = item)) +
  geom_col()+
  geom_text(aes(label = sugars), position=position_stack(vjust=0.5),color="black",size=3)+
  ggtitle("McDonald's Top 10 Item with Highest Sugar Content") +
  theme(legend.position="none")

highest_sugar
```

  Surprisingly, the list of items contains more shakes then desserts.

# Conclusion

  In conclusion, stay away from eggs and shakes.